Boosted

### 2015-10-30 boost_tree.rmd
finish forest and log

#clusters roughly break down to 1 day, 3 wks, 2.5m, 9m, 1.5yr, 3 yr, over 3 yr
# in cbrt days this is equivalent to breaks of 0,1,2,7589, 4.2358, 6.5, 8.183, 10.307, 14.1
#make new clusters:
all9a$b.timespan.cbrt<- cut(all9a$timespan.cbrt, 
                            breaks= c(0,2.7589, 4.2358, 6.5, 8.183, 10.307, 14.1), 
                            include.lowest=TRUE, 
                            labels= c("1d-3wk","3wk-2.5m", "2.5m-9m","9m-1.5y","1.5y-3y",">3y"))

@@

for(i in 1:1){

@@

        for (j in 1:8){
                #make boosted tree
                fit<-gbm(as.formula(formula), 
                         data=train[-folds[[j]],], distribution="bernoulli", n.trees= 10000,
                         shrinkage=0.001,interaction.depth=4,
                         n.minobsinnode = 20)

>>>>

#clusters roughly break down to 1 day, 3 wks, 2.5m, 9m, 1.5yr, 3 yr, over 3 yr
# in cbrt days this is equivalent to breaks of 0,1,2,7589, 4.2358, 6.5, 8.183, 10.307, 14.1
#make new clusters:
all9a$b.timespan.cbrt<- cut(all9a$timespan.cbrt, 
                            breaks= c(0,2.7589, 4.2358, 6.5, 8.183, 10.307, 14.1), 
                            include.lowest=TRUE, 
                            labels= c("1d-3wk","3wk-2.5m", "2.5m-9m","9m-1.5y","1.5y-3y",">3y"))
write.csv(all9a, 'C:/Users/n9232371/Documents/Consultbusiness/data/all9a.csv')

@@

@@

        for (j in 1:8){
                #make boosted tree
                fit<-gbm(as.formula(formula), 
                         data=train[-folds[[j]],], distribution="bernoulli", n.trees= 10000,
                         n.minobsinnode = 20)
